Load libraries
```{r}
library(tidyverse)
library(dplyr)
library(stringr)
library(janitor)
```

Load files
```{r}
movies <- read_csv("data/movies.csv")
tv <- read_csv("data/tvs.csv")
```

See summary
```{r}
glimpse(movies)
glimpse(tv)
```

Clean column names
```{r}
movies <- movies %>% 
  clean_names()

tv <- tv %>% 
  clean_names()
```

Get rid of one-line plot
```{r}
movies <- movies %>%
  select(-one_line)
```

Clean the year. Create start and end years
```{r}
movies <- movies %>%
  mutate(year = str_replace_all(year, "[^0-9–]", "")) %>%  # Remove non-numeric characters except dash
  separate(year, into = c("start_year", "end_year"), sep = "–", fill = "right") %>%
  mutate(across(c(start_year, end_year), as.numeric))  # Ensure numeric conversion

head(movies)
```

Separate genre column into multiple columns

```{r}
movies <- movies %>%
  mutate(genre = str_replace_all(genre, "[\n]", "")) %>%  # remove any newlines
  separate(genre, into = c("genre_1", "genre_2", "genre_3"), sep = ", ", fill = "right")
```

Separate directors and stars
```{r}
movies <- movies %>%
  mutate(stars = as.character(stars)) %>% # make stars col all characters
  mutate(stars = str_trim(stars)) %>% # trim spaces and newlines
  
  # make all rows have "Directors:" to get proper split
  mutate(stars = ifelse(str_detect(stars, "Directors?:"),
                        stars,  # if "Directors:" exists, keep as is
                        paste0("Directors: NA | ", stars)  # if missing, prepend "Directors: NA |"
  )) %>%
  
  # split into "directors" and "stars"
  separate(stars, into = c("directors", "stars"), sep = "\\|", extra = "merge", fill = "right") %>%
  # split directors into at most 2 columns
  separate(directors, into = c("director_1", "director_2"), sep = ", ", fill = "right") %>%
  # split stars into at most 4 columns
  separate(stars, into = c("star_1", "star_2", "star_3", "star_4"), sep = ", ", fill = "right") %>% 
  
  mutate(
    # remove "Director: " or "Directors: " and trim spaces/newlines
    director_1 = str_replace(director_1, "^(Director:\\s*|Directors:\\s*)", ""),
    director_1 = str_replace_all(director_1, "[\n\r]", ""),  # remove all newlines
    director_1 = str_trim(director_1),  # trim extra spaces
    
    # convert "NA" string into actual NA values
    director_1 = na_if(director_1, "NA"),
    star_1 = na_if(star_1, "NA"),
    
    # remove "Stars: " and any newlines or extra spaces
    star_1 = str_replace(star_1, "^\\s*Stars:", ""),  # remove "Stars:" with leading spaces
    star_1 = str_replace_all(star_1, "[\n\r]", " "),  # replace newlines with spaces
    star_1 = str_squish(star_1),  # remove extra spaces between words
    star_2 = str_replace_all(star_2, "[\n\r]", " "),
    star_2 = str_squish(star_2),
    star_3 = str_replace_all(star_3, "[\n\r]", " "),
    star_4 = str_squish(star_4),
    star_4 = str_replace_all(star_4, "[\n\r]", " "),
    star_4 = str_squish(star_4)
  )

# check first few rows
head(movies)
```

Clean gross col.
```{r}
movies <- movies %>% 
  mutate(
    gross = str_replace_all(gross, "[^0-9.]", ""),  # remove non-num chars except period
    gross = as.numeric(gross)  # convert to num
  )
```


## Check movies vs tv shows
Clean movies and tv names for better comparison.
```{r}
movies <- movies %>%
  mutate(
    movies = movies %>%
      tolower() %>%  # Convert to lowercase
      str_trim() %>%  # Trim spaces
      str_squish()  # Remove extra spaces
  )

tv <- tv %>%
  mutate(
    name = name %>%
      tolower() %>%  # Convert to lowercase
      str_trim() %>%  # Trim spaces
      str_squish()  # Remove extra spaces
  )
```


Filter out only tv shows and only movies
```{r}
tv_only <- movies %>% 
  filter(movies %in% tv$name)

head(tv_only)

movies_only <- movies %>%
  filter(!movies %in% tv$name)
```

### Further cleaning movies vs tv
Filter out rows in movies_only with "Reality-TV" tag
```{r}
# Move Reality-TV shows to tv_only
reality_tv <- movies_only %>%
  filter(genre_1 == "Reality-TV" | genre_2 == "Reality-TV" | genre_3 == "Reality-TV")

# Remove Reality-TV rows from movies_only
movies_only <- anti_join(movies_only, reality_tv, by = "movies")

# Add Reality-TV shows to tv_only
tv_only <- bind_rows(tv_only, reality_tv)
```

Filter from not one-year
```{r}
# Identify rows where start_year and end_year are different and both exist
multi_year_tv <- movies_only %>%
  filter((!is.na(start_year)) & (!is.na(end_year)) & (start_year != end_year))

# Remove these rows from movies_only
movies_only <- anti_join(movies_only, multi_year_tv, by = "movies")

# Add these rows to tv_only
tv_only <- bind_rows(tv_only, multi_year_tv)
```

Filter out shorts and commercials
```{r}
movies_only %>% 
  filter(genre_1 == "Short" | genre_2 == "Short" | genre_3 == "Short")
```

Combine two dataframes
```{r}
movies_cleaned <- bind_rows(
  movies_only %>% mutate(type = "movie"),
  tv_only %>% mutate(type = "tv")
)

movies_cleaned <- movies_cleaned %>% 
  rename(name = movies)

movies_cleaned
```

Create shorts column
```{r}
wrong_movies <- movies_cleaned %>% 
  mutate(type = if_else(
    genre_1 == "Short" | genre_2 == "Short" | genre_3 == "Short", 
    "Short",
    type  # Keep existing value if condition is FALSE
  ))
```

```{r}
filter(movies_cleaned, type == "Short")
```

